### 2020-07-27 theory/notes_banks_buyingfinitemajorities.tex
incorporate additional notes on banks

$$ \sum_{i \in C} \max{0, a_i + v_i} \geq W_B$$

@@

\begin{equation}
\label{eqn:solution}
min\{S(a) : a \in U(\mathbf{v}, W_B) \}
\end{equation}

@@

Banks then proceeds to show that there are monotonic bribing schedules contained within the solution for equation \ref{eqn:solution}. For any $a \in \real$ let $k(a) = \lvert C(a) \rvert$. Suppose that $a\in U^l(\mathbf{v}, W_B)$ is such that $v_i \geq v_j$ and $j \in C(a)$ but $i \notin C(a)$. Then, under $A_2$, there exists $a' \in U^l(\mathbf{v}, W_B)$ with $S(a') \leq S(a)$, $k(a') = k(a)$ and $i \in C(a')$ but $j \notin C(a')$ by simply swapping $i$ for $j$.\footnote{Note that since $v_i \geq v_j$, we have that $t(a) - v_i \leq  t(a) - v_j$, i.e. $a'_i \leq a_j$. $A_2$ guarantees that $a'_i$ or $a_j$ are non-negative.}

@@

Note that the choice of $k(a)$ and $t(a)$ fully characterize any schedule $a \in U_m^l(\mathbf{v}, W_B$. We can thus fully characterize the optimization problem of $A$ as

@@

subject to the constraint that the induced schedule $a \in U_m^l$. Banks then reformulates this as an unconstrained problem by noting the following. First, if $a(k, t, \mathbf{v})$ is unbeatable, it must be that $k \geq (n + 1)/2$, so by $A_1$ it must be that if $a_i(k, t, \mathbf{v}) = 0$, then $v_i < 0$. Therefore, $B$ receives all non-bribed voters for free. For $a(k, t, \mathbf{v})$ to be unbeatable, then, it must be that $B$ cannot afford the remaining $(n + 1)/2 - (n - k)$

>>>>

$$ \sum_{i \in C} \max\{0, a_i + v_i\} \geq W_B$$

@@

\begin{equation}
\label{eqn:solution}
\min_a\{S(a) : a \in U(\mathbf{v}, W_B) \}
\end{equation}

@@

Banks then proceeds to show that there are monotonic bribing schedules contained within the solution for equation \ref{eqn:solution}. For any $a \in \real$ let $k(a) = \lvert C(a) \rvert$. Suppose that $a\in U^l(\mathbf{v}, W_B)$ is such that $v_i \geq v_j$ and $j \in C(a)$ but $i \notin C(a)$. Then, under $A_2$, there exists $a' \in U^l(\mathbf{v}, W_B)$ with $S(a') \leq S(a)$, $k(a') = k(a)$ and $i \in C(a')$ but $j \notin C(a')$ by simply swapping $i$ for $j$.\footnote{Note that since $v_i \geq v_j$, we have that $t(a) - v_i \leq  t(a) - v_j$, i.e. $a'_i \leq a_j$. $A_2$ guarantees that $a'_i$ and $a_j$ are non-negative.}

@@

Note that the choice of $k(a)$ and $t(a)$ fully characterize any schedule $a \in U_m^l(\mathbf{v}, W_B)$. We can thus fully characterize the optimization problem of $A$ as

@@

subject to the constraint that the induced schedule $a \in U_m^l$. Banks then reformulates this as an unconstrained problem by noting the following. First, if $a(k, t, \mathbf{v})$ is unbeatable, it must be that $k \geq (n + 1)/2$, so by $A_1$ it must be that if $a_i(k, t, \mathbf{v}) = 0$, then $v_i < 0$. Therefore, $B$ receives all non-bribed voters for free. For $a(k, t, \mathbf{v})$ to be unbeatable, then, it must be that $B$ cannot afford the remaining $(n + 1)/2 - (n - k) = k - (n - 1)/2$ voters, or

$$t * (k - (n - 1)/2) \geq W_B$$

Solving this for equality yields the optimal transfer from $A$ to members of $C(A) = \{1, ..., k\}$, conditional on k:

\begin{align}
    \label{eqn:common_transfer}
    t(k, W_B) = \frac{W_B}{k - (n - 1)/2}
\end{align}

Defining minimal winning expenditures as

\begin{align}
    \label{eqn:total_expenditure}
    E(k, \mathbf{v}, W_B) = k \cdot t(k, W_B) - \sum_{i \leq k} v_i
\end{align}

we can state $A$'s problem as

\begin{align}
\label{eqn:minimal_expenditure}
\min_k \{E(k, \mathbf{v}, W_B) : k \in {(n + 1/2), ..., n}\}
\end{align}

Denote the solution to expression \ref{eqn:minimal_expenditure} as $k^*(\mathbf{v}, W_B)$. This solution genenerates a solution to expression \ref{eqn:solution}

\section{Results}

First, characterize a solution for $k^*$. Because $k$ is finite, calculus cannot be employed. Instead, we deploy a discrete version of these techniques. First let's define $\Delta(k) = E(k + 1) - E(k)$ as the difference in expenditure from adding another coalition member. Note that if $\Delta(k) \geq 0$ then $A$ does not want to add another member to the coalition. Conversely, if $\Delta(k) < 0$, then $A$ is strictly better off by adding the $k + 1$th member of the coalition.

Next, suppose that $\Delta(k)$ is increasing in $k$. The following algorithm can then be used to identify $k^*$: if $\Delta((n + 1)/2) \geq 0$, then we know from $]\Delta(k)$ increasing that $A$ is better off by setting $k^*$ to $(n + 1)/2$. If $\Delta((n + 1)/2) < 0$, then we know that $k^*$ must be greater than $(n + 1)/2$, so we next solve for $\Delta((n + 3)/2)$, and so on.

We can therefore search for the optimal $k^*$ with the following algorithm:

\begin{align}
    k^* = 
    \begin{cases}
        (n + 1)/2 & \text{if } \Delta((n + 1)/2) \geq 0 \\
        \max\{k : \Delta(k - 1) < 0\} & \text{otherwise}
    \end{cases}
\end{align}

Banks also shows that $\Delta(k)$ is indeed nondecreasing.

\begin{align}
    \Delta(k)  & = \left[\frac{(k + 1)W_B}{k + 1 - (n - 1)/2} - \sum_{i \leq k + 1}v_i \right]\\
    & = \frac{-W_B (n - 1)}{2(k + 1 - (n - 1)/2)(k - (n - 1)/2)} - v_{k + 1}\\
    & \equiv T(k, W_B) - v_{k + 1}
\end{align}
